\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-06-25 coqimpl.tex

Final Field a' : nat := 1.
Field c : a@\YZ{should this be a'?}@ = 1 := eq_refl.
Field add : nat -> nat -> nat := (+).
Fail Field comm_add : ...

Family MonotonicF.
  Final Field f : nat -> nat := non_impl.
  Field p : monotonic f := non_impl.
SealFamily.

EndFamily.
\end{minted}
  \end{minipage}
\begin{minipage}[t]{0.45\linewidth}
\begin{minted}[fontsize=\footnotesize,escapeinside=@@]{Coq}
Family I2 extends I.
Override Field a : nat := 1. (* Override *)
Inherit b.                   (* Inherit  *)

@@

Override Field add := (-).@\YZ{'add' is not a good choice of name---it doesn't make sense to override add with subtraction.}@

Inherits Until MonotonicF.
Override Family MonotonicF.
  Final Field f : nat@\YZ{nat -> nat ?}@ := (+ 1).
  Field p : monotonic f := ...
SealFamily. 
EndFamily.
\end{minted}
  \end{minipage}
  \caption{Example Code for Inheritance and Reasoning}\label{fig:plugin-example3}
\end{figure}

>>>>

Final Field a' : nat := 1.
Field c : a'@\YZ{should this be a'?}\EDJreply{Yes Thanks.}@ = 1 := eq_refl.
Field bop : nat -> nat -> nat := (+).
Fail Field comm_add : ...

 Family MonotonicF.
  Final Field f : nat -> nat := non_impl.
  Field p : monotonic f := non_impl.
 SealFamily. 
EndFamily.
\end{minted}
  \end{minipage}
\begin{minipage}[t]{0.45\linewidth}
\begin{minted}[fontsize=\footnotesize,escapeinside=@@]{Coq}
Family I2 extends I.
 Override Field a : nat := 1. (* Override *)
 Inherit b.                   (* Inherit  *)

@@

Override Field bop := (-).@\YZ{'add' is not a good choice of name---it doesn't make sense to override add with subtraction.}\EDJreply{Changed to b(inary)op now}@

Inherits Until MonotonicF.
Override Family MonotonicF.
  Final Field f : nat@\YZ{nat -> nat ?}@ := (+ 1).

  Field p : monotonic f := ...
 SealFamily. 
EndFamily.
\end{minted}
  \end{minipage}
  \caption{Example Code for Inheritance and Reasoning}\label{fig:plugin-example3}
\end{figure}
